Embedding Intuitionistic into Classical Logic

### 2022-10-10 FoSSaCS/fossacs-EIICL.tex
Update fossacs-EIICL.tex

\begin{definition}
	A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$ and $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
	A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC} (Classical Propositional Calculus).
\end{definition}

@@

\begin{definition}
	A \emph{Kripke structure} $\mathcal K = (W, (v_w)_{w\in W})$ consists of a partially ordered set $W$ of \emph{worlds}, called the Kripke \emph{frame}, and a family of valuations $(v_w)_{w\in W}$ such that $v_u(A)\leq v_u(A)$ for all $u\leq w$ and propositional variables $A$ (this is called the \emph{persistency condition}).
	The model relation between the $v_u$ and formulas $\varphi$ is defined as before, except in the case of implications, where we set
	\begin{itemize}
		\item $v_u\models\varphi\to \psi$ if for all $w\geq u$ we have $w\not\models\varphi$ or $u\models\psi$.
	\end{itemize}
	We say that $\varphi$ is satisfied at a world $u$ if $v_u\models\varphi$ and write $u\models\varphi$. If a formula is satisfied at every world then $\mathcal K$ is a \emph{model} for $\varphi$. A formula is valid if every Kripke structure is a model of it. We denote the set of valid formulas with \emph{IPC} (Intuitionistic Propositional Calculus).
\end{definition}
There are many classical tautologies which are not intuitionistically valid, e.g. the law of excluded middle $A\vee\neg A$. On the other hand any intuitionistic theorem is a classical one.

@@

\begin{definition}
	Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
	m, &\text{if $b=a$,}\\
	v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$, $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$, $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$, $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\varphi$ is satisfiable if there exist $\mathcal M, v$  with $\mathcal M, v\models\varphi$. A $\Sigma$-structure $\mathcal M$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$, we write $\mathcal M\models\varphi$. A formula is valid if every $\Sigma$-structure $\mathcal M$ satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$} and $R^{I_w}|_{M_u} = R^{I_u}$.
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$, $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$, $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$, $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. $\varphi$ is valid if it is satisfied by every Kripke structure.
	$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.

@@

\begin{lemma}\label{lemma:propositional-normal-form}
	For every propositional formula $\varphi$ there exists an atom $P$ as well as sets of clauses $\mathcal R, \mathcal X$, with $\mathcal R$ containing  \emph{flat clauses} of the form
	$$\bigwedge_iA_i\to\bigvee_jB_j$$
	and $\mathcal X$ containing \emph{implication clauses} of the form
	$$(A\to B)\to C,$$
	such that $\varphi$ is intuitionistically equivalid to
	$$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$where $A_i, B_i, A, B, C$ are atomic. This size of $\mathcal R$ and $\mathcal X$ is linear in the size of $\varphi$. In general they will contain additional propositional variables.
\end{lemma}

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively:
	\begin{itemize}
		\item $\bot^u = \bot$.
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the theory of Kripke structures, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w)\:|\: \text{ $A$ occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{r}$$
	where $r$ is a new constant symbol.
\end{definition}

@@

This is somewhat unsatisfying as we end up in a much more complex logic. However using the normal form from Lemma~\ref{lemma:propositional-normal-form}, i.e. assuming that $\varphi$ is of the form $$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$ for some flat clauses $\mathcal R$ and implicational clauses $\mathcal X$, further simplification is possible:
\begin{itemize}
	\item For flat clauses $(\bigwedge A_i\to\bigvee B_j)^u$ is
	$$\forall w\left(u\preceq w\to\bigwedge_i A_i(u)\to\bigvee_jB_j(u)\right).$$
	\item For implication clauses $((A\to B)\to C)^u$ is
	$$\forall w(u\preceq w\to(\forall k(w\preceq k\to A(k)\to B(k)))\to C(w))$$
\end{itemize}

and after applying Herbrandization we end up with a formula $$\varphi^{CH} = K(\varphi)\to r\preceq s\to\left(\bigwedge\mathcal R^{uS}\wedge \bigwedge\mathcal X^{uS}\right)\to P(s)$$ where $s$ is a new constant symbol, each formula in $\mathcal R^{uS}$ is of the form
$$\forall w\left(s\preceq w\to\bigwedge_iA_i(u)\to\bigvee_jB_j(u)\right)$$
and each formula $\psi\in\mathcal X^{uS}$ is of the form
$$\forall w(s\preceq w\to(w\preceq f_\psi(w)\to A(f_\psi(w))\to B(f_\psi(w)))\to C(w))$$
with $f_\psi$ being a new function symbol.

@@

\begin{definition}
For $\psi\in\mathcal X$ let $[\psi]$ denote the corresponding clause in $\mathcal X^{uS}$. Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^{CH}$.
We say $(A\to B)\to C\in\mathcal X$ is \emph{fulfilled} at $m\in M$ iff $A^I(m)\to B^I(m)$ is false or $C^I(m)$ is true. For $\psi\in\mathcal X$ define $$g_\psi : M\to M, m\mapsto\begin{cases}
		m,&\text{ if $\psi$ is fulfilled at $u$,}\\
		f^I_{\lbrack\psi\rbrack}(m),&\text{ else.}		
	\end{cases}$$Define a model $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal X$.
		\item $r^{I_T} = s^{I_T} = \epsilon$.
		\item Interpret $\preceq$ as the prefix-order.
		\item We set $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n, &\text{if $\psi$ occurs in $[\psi_1]\dots[\psi_n]$,}\\
			\psi_1\dots\psi_n\psi, &\text{else.}			
		\end{cases}$$
		\item For propositional variables $P$, we set $$P^{I_T}\left(\psi_1\dots \psi_n\right) = P^I\left(g_{\psi_n}\left(\dots\left(g_{\psi_1}\left(s^I\right)\right)\dots\right)\right).$$
	\end{itemize}
\end{definition}
\begin{lemma}~\label{thm:prop-countermodel-reduction}
	Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^{CH}$.
	\begin{enumerate}
		\item $\psi$ is fulfilled at $f_{[\psi]}^I(u)$ for all $u\in M, \psi\in\mathcal X$.
		\item If $\psi$ is fulfilled at some $m\in M$ then $\psi$ is fulfilled at all $n\succeq m$.
	\end{enumerate}
\end{lemma}

@@

We can apply the previous results to give a direct embedding from intuitionistic into classical propositional logic. We know that $\varphi^{CH}$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x, &\text{ if $\psi$ occurs in $x$,}\\
	x\psi, &\text{ otherwise.}
\end{cases}$$
Now we can replace every $\forall$-quantifier in $\varphi^{CH}$ by enumerating all the ground terms, and then replace all distinct ground instances of relations by new propositional variables yielding a propositional formula. Note that the encoding of partial order becomes redundant with this so we drop it, but we need to keep the persistency restraints. This gives us the following theorem:

\begin{theorem}
	Suppose we are given a formula as in Lemma~\ref{lemma:propositional-normal-form}, i.e. of the form
	$$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal S\right)\to P$$
	with flat $\mathcal R$ and implication $\mathcal S$. Let $\Lambda$ denote the set of sequences without repetition over $\mathcal X$. For every propositional variable $A$ and $\lambda\in\Lambda$ consider a new propositional Variable $X^\lambda$. Define $R^\#$ as the union over all sets
	$$
		\left\{\bigwedge_iA_i^\lambda\to\bigvee_jB_j^\lambda\:|\:\lambda\in\Lambda\right\}
	$$
	for $\bigwedge_iA_i\to\bigvee_jB_j\in\mathcal R$ and $\mathcal X^\#$ as the union over all sets
	$$
		\left\{\left({A^\lambda\psi} \to A^{\lambda\psi}\right)\to(C^\lambda)\:|\:\lambda\in\Lambda, \psi\text{ does not occur in }\lambda\right\}
	$$
	for $\psi = (A\to B)\to C\in\mathcal X$ as well as $P^\#$ as the union over all sets
	$$
		\left\{A^\lambda\to A^{\lambda\psi}\:|\:\lambda\in\Lambda, \psi\psi\text{ does not occur in }\lambda\right\}
	$$
	 for each propositional variable $A$ occurring in $\varphi$ encoding persistency. Then
	$$
		\varphi^\# := \left(\bigwedge P^\#\wedge\bigwedge \mathcal R^\#\wedge\bigwedge\mathcal X^\#\right)\to P^\epsilon
	$$
	is classically valid if and only if $\varphi$ is intuitionistically valid.
\end{theorem}
%\begin{theorem}
%	$\bigwedge\mathcal S\to P$ is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset$ is classically valid.
%\end{theorem}

@@

Suppose we are given a formula $\varphi$ in normal form $$\left(\bigwedge R\wedge\bigwedge X\right)\to P$$ as in Lemma~\ref{lemma:propositional-normal-form}. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a polynomially-sized formula is: Instead of expressing validity at every node of $\mathcal M_T$ --- which was done in the CPC translation --- we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $X_\psi$ in the next definition handle the branching, i.e. express which path is considered.

>>>>

\begin{definition}
	A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$, $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
	A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC} (Classical Propositional Calculus).
\end{definition}

@@

\begin{definition}
	A \emph{Kripke structure} $\mathcal K = (W, (v_w)_{w\in W})$ consists of a partially ordered set $W$ of \emph{worlds}, called the Kripke \emph{frame}, and a family of valuations $(v_w)_{w\in W}$ such that $v_u(A)\leq v_u(A)$ for all $u\leq w$ and propositional variables $A$ (this is called the \emph{persistency condition}).
	The model relation between the $v_u$ and formulas $\varphi$ is defined as before, except in the case of implications, where we set
	\begin{itemize}
		\item $v_u\models\varphi\to \psi$ iff for all $w\geq u$ we have $w\not\models\varphi$ or $u\models\psi$.
	\end{itemize}
	We say that $\varphi$ is satisfied at a world $u$ if $v_u\models\varphi$ and write $u\models\varphi$. If a formula is satisfied at every world then $\mathcal K$ is a \emph{model} for $\varphi$. A formula is valid if every Kripke structure is a model of it. We denote the set of valid formulas with \emph{IPC} (Intuitionistic Propositional Calculus).
\end{definition}
There are many classical tautologies which are not intuitionistically valid, e.g. the law of excluded middle $A\vee\neg A$. On the other hand any intuitionistic theorem is a classical one.

@@

\begin{definition}
	Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
	m, &\text{if $b=a$,}\\
	v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$, $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\varphi$ is satisfiable if there exist $\mathcal M, v$  with $\mathcal M, v\models\varphi$. A $\Sigma$-structure $\mathcal M$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$, we write $\mathcal M\models\varphi$. A formula is valid if every $\Sigma$-structure $\mathcal M$ satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, called the Kripke \emph{frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$ we have $M_u\subseteq M_w$, $f^{I_w}|_{M_u} = f^{I_u}$ and $R^{I_w}|_{M_u} = R^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
	The model relation between $\mathcal M_u$, $v$ (targeting $\mathcal M_u$) and formulas $\varphi$ is defined as before, except in the cases of implication and $\forall$-quantification, where we set
	\begin{itemize}
		\item $\mathcal M_u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $\mathcal M_u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	We write $u, v\models\varphi$ if $\mathcal M_u, v\models \varphi$. $\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. If such $\mathcal K$ exists then $\varphi$ is satisfiable. $\varphi$ is valid if it is satisfied by every Kripke structure.
	$\varphi$ is valid for some frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.

@@

\begin{lemma}\label{lemma:propositional-normal-form}
	For every propositional formula $\varphi$ there exists an atom $P$ as well as sets of clauses $\mathcal R, \mathcal X$, with $\mathcal R$ containing  \emph{flat clauses} of the form
	$$\bigwedge_iA_i\to\bigvee_jB_j$$
	and $\mathcal X$ containing \emph{implication clauses} of the form
	$$(A\to B)\to C,$$
	such that $\varphi$ is intuitionistically equivalid to
	$$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$where $A_i, B_i, A, B, C$ are atomic. The size of $\mathcal R$ and $\mathcal X$ is linear in the size of $\varphi$. In general they will contain additional propositional variables.
\end{lemma}

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively:
	\begin{itemize}
		\item $\bot^u = \bot$.
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the theory of Kripke structures, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w)\:|\: \text{ $A$ occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \forall u\varphi^{u}.$$
\end{definition}

@@

This is somewhat unsatisfying as we end up in a much more complex logic. However using the normal form from Lemma~\ref{lemma:propositional-normal-form}, i.e. assuming that $\varphi$ is of the form $$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$ for some flat clauses $\mathcal R$ and implicational clauses $\mathcal X$, further simplification is possible:
\begin{itemize}
	\item For flat clauses $(\bigwedge A_i\to\bigvee B_j)^u$ is
	$$\forall w\left(u\preceq w\to\bigwedge_i A_i(w)\to\bigvee_jB_j(w)\right).$$
	\item For implication clauses $((A\to B)\to C)^u$ is
	$$\forall w(u\preceq w\to(\forall k(w\preceq k\to A(k)\to B(k)))\to C(w))$$
\end{itemize}

and after applying Herbrandization we end up with a formula $$\varphi^{CH} = K(\varphi)\to\left(\bigwedge\mathcal R^{uS}\wedge \bigwedge\mathcal X^{uS}\right)\to P(s)$$ where $s$ is a new constant symbol, each formula in $\mathcal R^{uS}$ is of the form
$$\forall w\left(s\preceq w\to\bigwedge_iA_i(w)\to\bigvee_jB_j(w)\right)$$
and each formula $\psi\in\mathcal X^{uS}$ is of the form
$$\forall w(s\preceq w\to(w\preceq f_\psi(w)\to A(f_\psi(w))\to B(f_\psi(w)))\to C(w))$$
with $f_\psi$ being a new function symbol.

@@

\begin{definition}
For $\psi\in\mathcal X$ let $[\psi]$ denote the corresponding clause in $\mathcal X^{uS}$. Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^{CH}$.
We say $(A\to B)\to C\in\mathcal X$ is \emph{fulfilled} at $m\in M$ iff $A^I(m)\to B^I(m)$ is false or $C^I(m)$ is true. For $\psi\in\mathcal X$ define $$g_\psi : M\to M, m\mapsto\begin{cases}
		m,&\text{ if $\psi$ is fulfilled at $u$,}\\
		f^I_{\lbrack\psi\rbrack}(m),&\text{ else.}		
	\end{cases}$$Define a model $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal X$.
		\item $s^{I_T} = \epsilon$.
		\item Interpret $\preceq$ as the prefix-order.
		\item We set $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n, &\text{if $\psi$ occurs in $[\psi_1]\dots[\psi_n]$,}\\
			\psi_1\dots\psi_n\psi, &\text{else.}			
		\end{cases}$$
		\item For propositional variables $P$, we set $$P^{I_T}\left(\psi_1\dots \psi_n\right) = P^I\left(g_{\psi_n}\left(\dots\left(g_{\psi_1}\left(s^I\right)\right)\dots\right)\right).$$
	\end{itemize}
\end{definition}
\begin{lemma}~\label{thm:prop-countermodel-reduction}
	Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^{CH}$.
	\begin{enumerate}
		\item $\psi$ is fulfilled at $f_{[\psi]}^I(u)$ for all $u\in M, \psi\in\mathcal X$.
		\item If $\psi$ is fulfilled at some $m\in M$ then $\psi$ is fulfilled at all $n\succeq m$.
	\end{enumerate}
\end{lemma}

@@

We can apply the previous results to give a direct embedding from intuitionistic into classical propositional logic. We know that $\varphi^{CH}$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x, &\text{ if $\psi$ occurs in $x$,}\\
	x\psi, &\text{ otherwise.}
\end{cases}$$
Now we can replace every $\forall$-quantifier in $\varphi^{CH}$ by enumerating all the ground terms, and then replace all distinct ground instances of relations by new propositional variables yielding a propositional formula. Note that the encoding of partial order becomes redundant with this so we drop it, but we need to keep the persistency constraints. This gives us the following theorem:

\begin{theorem}
	Suppose we are given a formula as in Lemma~\ref{lemma:propositional-normal-form}, i.e. of the form
	$$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal S\right)\to P$$
	with flat $\mathcal R$ and implication $\mathcal S$. Let $\Lambda$ denote the set of sequences without repetition over $\mathcal X$. For every propositional variable $A$ and $\lambda\in\Lambda$ consider a new propositional Variable $A^\lambda$. Define $R^\#$ as the union over all sets
	$$
		\left\{\bigwedge_iA_i^\lambda\to\bigvee_jB_j^\lambda\:|\:\lambda\in\Lambda\right\}
	$$
	for $\bigwedge_iA_i\to\bigvee_jB_j\in\mathcal R$ and $\mathcal X^\#$ as the union over all sets
	$$
		\left\{\left(A^{\lambda\psi} \to A^{\lambda\psi}\right)\to(C^\lambda)\:|\:\lambda\in\Lambda, \psi\text{ does not occur in }\lambda\right\}
	$$
	for $\psi = (A\to B)\to C\in\mathcal X$ as well as $P^\#$ as the union over all sets
	$$
		\left\{A^\lambda\to A^{\lambda\psi}\:|\:\lambda\in\Lambda, \psi\psi\text{ does not occur in }\lambda\right\}
	$$
	 for each propositional variable $A$ occurring in $\varphi$ encoding persistency. Then
	$$
		\varphi^\# := \left(\bigwedge P^\#\wedge\bigwedge \mathcal R^\#\wedge\bigwedge\mathcal X^\#\right)\to P^\epsilon
	$$
	is classically valid if and only if $\varphi$ is intuitionistically valid.
\end{theorem}
%\begin{theorem}
%	$\bigwedge\mathcal S\to P$ is intuitionistically valid iff $\bigwedge\mathcal S^\#\to P^\emptyset$ is classically valid.
%\end{theorem}

@@

Suppose we are given a formula $\varphi$ in normal form $$\left(\bigwedge\mathcal R\wedge\bigwedge\mathcal X\right)\to P$$ as in Lemma~\ref{lemma:propositional-normal-form}. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a polynomially-sized formula is: Instead of expressing validity at every node of $\mathcal M_T$ --- which was done in the CPC translation --- we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $X_\psi$ in the next definition handle the branching, i.e. express which path is considered.

\begin{definition}
	For every propositional variable $A$ occurring in $\varphi$ and non-negative integer $n$ consider a new propositional variable $A^n$ and for every formula $\psi\in\mathcal X$ consider a new propositional variable $X_\psi^n$. Let $\vec A^n$ range over all propositional variables $A^n$ and $\vec X^n$ range over all $X_\psi^n$. Define
	\begin{itemize}
		\item {\normalfont Valid}$(n)$ which encodes that $\vec X^n_\psi$ represents a valid next element of a sequence without repetition, i.e. if we interpret the $\vec X^i$ as bit-vectors, then $\vec X^n$ has exactly one bit set to $1$, indicating the formula at the $n$-th position of the sequence, and it is at a position that is $0$ in $\sum\{\vec X^i\:|\:i < n\}$.
		\item {\normalfont Persistent}$(n)$ which encodes that the persistency condition holds.
		\item {\normalfont Sat}$_{\mathcal R}(n)$ encoding that the formulas in $\mathcal R$ hold at the $n$-th world of the path.
		\item {\normalfont Sat}$_{\mathcal X}(n)$ encoding that the formula in $\mathcal X$ that is represented by $\vec X^{n-1}$ holds.
	\end{itemize}
	Have $k = |\mathcal X|$ and define$$\varphi^Q_{i} = \exists \vec A^i\forall \vec X^i\left(\text{\normalfont Persistent}(i)\wedge \text{\normalfont Sat}_{\mathcal R}(i)\wedge \text{\normalfont Sat}_{\mathcal X}(i)\wedge\left(\text{\normalfont Valid}(i)\to \varphi^Q_{i+1}\right)\right)$$
	for $0 < i < k$, as well as the special cases
	$$\varphi^Q_{k} = \exists \vec A^k\left(\text{\normalfont Persistent}(k)\wedge \text{\normalfont Sat}_{\mathcal R}(k)\wedge \text{\normalfont Sat}_{\mathcal X}(k)\right)$$
	for leafs, and $$\varphi^Q = \varphi_0^Q = \exists \vec A^0\forall \vec X^0\left(\neg P^0\wedge \text{\normalfont Sat}_{\mathcal R}(0)\wedge(\text{\normalfont Valid}(0)\to \varphi_1^Q)\right)$$for the root.
	Example encodings of the above formulas are:
	\begin{align*}
		\text{\normalfont Valid}(n) = &\left(\bigvee\left\{X^n_\psi\:|\:\psi\in\mathcal X\right\}\right)\wedge\left(\bigwedge \left\{\neg(X^n_{\psi_1}\wedge X^n_{\psi_2})\:|\:\psi_1\neq\psi_2\in\mathcal X\right\}\right)\wedge\\&\left(\bigwedge\left\{\bigwedge\{X^i_\psi\to\neg X^n_\psi\:|\:i < n\}\:|\:\psi\in\mathcal X\right\}\right)\\
		\text{\normalfont Persistent}(n) = & \bigwedge\left\{A^{n-1}\to A^n\:|\: A \text{ prop. variable with }A^{n-1}\in\vec A^{n-1}, A^n \in\vec A^{n}\right\}\\
		\text{\normalfont Sat}_{\mathcal R}(n) = &\bigwedge\left\{\bigwedge A^n_i\to\bigvee B^n_j\:|\:\bigwedge_i\mathcal R\right\}\\
		\text{\normalfont Sat}_{\mathcal X}(n) = & \bigwedge\left\{X^{n-1}_\psi\to (A^n\to B^n)\to C^{n-1}\:|\:\psi = (A\to B)\to C\in\mathcal X\right\}
	\end{align*}
\end{definition}
